Improving the communication and transparency of stock assessment using interactive

### 2018-11-08 manuscript.Rmd
Rough out two new sections by re-structuring some previous text

In the age of data-intensive science and big data, scientists across many fields are faced with the challenge of synthesizing and communicating information from large and complex data sets. Scientific data are often presented as tabular summaries and static plots, however, seeing patterns in tables can be difficult and static plots preclude detailed explorations of the underlying data. New open source tools are bridging this gap by making it easier to build interactive figures [@perkel2018]. In particular, browser-based data visualizations have been playing an increasing prominent role in communicating information on a wide range of topics. Interactive graphics are frequently utilized by media outlets, such as the New York Times, and scientists from a wide range of disciplines are starting to apply interactive visualization tools to explore and communicate their results [@yeatman2018; @tushar2017; @wick2015]. This trend has been fueled by the development of JavaScript libraries (e.g. D^3^ [@bostock2011], plotly [@plotly], leaflet [@leaflet], highcharts [@highcharts]) that enable the production of dynamic and interactive data visualizations in modern web-browsers. Interfaces to JavaScript libraries have also been developed to allow interactive plots to be coded using commonly used languages such as R [@R] or Python [@python]. By laying the technical infrastructure for creating interactive graphics, these new tools are ushering in a new era of Big Data by facilitating the exploration and communication of complex data and models.

The field of fisheries research has a long history of collecting and synthesizing a plethora of data using state-of-the-art computational technologies [@megrey2008]. Fisheries science has evolved alongside the rise of the computing era, and as tools improve so does the management advice provided by fisheries scientists. This management advice generally culminates from a stock assessment process whereby various sources of data and statistical methods are used to model the history, current status and future status of one or more fish stocks [@hilborn1992]. Recent advances in computational technologies have streamlined the process of stock assessment by facilitating the development and application of integrated stock assessment models [@maunder2013]. This means that analyses that were once carried out independently on different data sets can now be integrated into the one analysis by using statistical modeling tools such as JAGS [@plummer2003], AD Model Builder [@fournier2012] and Template Model Builder [@kristensen2015]. From a computational perspective, analyses of a variety of large data sets has never been easier. However, from a human perspective, contemporary stock assessment biologists are faced with the challenge managing data from a variety of sources and also understanding the algorithms that convert these data to advice for fisheries managers.

Note: still not liking the flow between the first and second paragraph. Still seems like I need to cut to the chase sooner...how can interactive visuals help?

@@

...need to get to the point here quicker...what is the problem and how can interactive visualization tools help?

>>>>

In the age of data-intensive science and big data, scientists across many fields are faced with the challenge of synthesizing and communicating information from large and complex data sets. Scientific data are often presented as tabular summaries and static plots, however, seeing patterns in tables can be difficult and static plots preclude detailed explorations of the underlying data. New open source tools are bridging this gap by making it easier to build interactive figures [@perkel2018]. In particular, browser-based data visualizations have been playing an increasing prominent role in communicating information on a wide range of topics. Interactive graphics are frequently utilized by media outlets, such as the FiveThirtyEight, and scientists from a wide range of disciplines are starting to apply interactive visualization tools to explore and communicate their results [@yeatman2018; @tushar2017; @wick2015]. This trend has been fueled by the development of JavaScript libraries (e.g. D^3^ [@bostock2011], plotly [@plotly], leaflet [@leaflet], highcharts [@highcharts]) that enable the production of dynamic and interactive data visualizations in modern web-browsers. Interfaces to JavaScript libraries have also been developed to allow interactive plots to be coded using commonly used languages such as R [@R] or Python [@python]. By laying the technical infrastructure for creating interactive graphics, these new tools are ushering in a new era of Big Data by facilitating the exploration and communication of complex data and models.

The field of fisheries research has a long history of collecting and synthesizing a plethora of data using state-of-the-art computational technologies [@megrey2008]. Fisheries science has evolved alongside the rise of the computing era, and as tools improve so does the management advice provided by fisheries scientists. This management advice generally culminates from a stock assessment process whereby various sources of data and statistical methods are used to model the history, current status and future status of one or more fish stocks [@hilborn1992]. Recent advances in computational technologies have streamlined the process of stock assessment by facilitating the development and application of integrated assessment models [@maunder2013]. This means that analyses that were once carried out independently on different data sets can now be integrated into the one analysis by using statistical modeling tools such as JAGS [@plummer2003], AD Model Builder [@fournier2012] and Template Model Builder [@kristensen2015]. From a computational perspective, analyses of a variety of large data sets has never been easier. However, from a human perspective, contemporary stock assessment biologists are faced with the challenge of managing data from a variety of sources and also understanding the algorithms that convert these data to advice for fisheries managers. Here we aim to demonstrate how interactive visualization tools provide an efficient and effective means of exploring and communicating the ever expanding array of data inputs and model outputs. First, we focus on data sets that are commonly used in stock assessment and provide one example where an interactive maps were used to simplify the detailed exploration of data from a long-term tagging program. Second, we focus on the modeling aspect of stock assessment and, again, we use an example to demonstrate how dynamic and interactive data visualizations can be used to explore, diagnose and communicate results from an integrated assessment model.

## Data

## Models

# Other draft text

@@
